Viscous Transport in Eroding Porous Media

### 2019-06-10 docs/transport/erosion_transport.tex
working on results

In~\cite{qua-moo2018}, we observed that erosion causes the space
between nearly touching bodies to quickly expand, and flat faces develop
along the region of near contact.  This qualitative behavior is also
observed In Figure~\ref{fig:Eroding20vort}, such as between bodies 3
\&4 and 15 \& 16.  However, by resolving bodies that are
much closer to one another when compared to our previous
work~\cite{qua-moo2018}, we see that it is possible for very little
erosion to occur between a pair of bodies.  In particular, for pairs of
bodies where the channel between the bodies is nearly perpendicular to
the main flow direction (bodies 1 \&6, 3 \& 9, and 13 \& 15), there is
very little shear stress and the effect of erosion is slight.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense101} \\
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense301}
%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
  with the fixed pressure drop condition. The color is the vorticity of
  the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
  256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
  and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In
  the forth frame, bodies 4, 12, and 17 have vanished completely, and
  body 19 has almost completely eroded.}
\end{center}
\end{figure}
{\color{red} 
In~\cite{qua-moo2018} we reported the quick expanding space at
the narrow channel between neighboring bodies, the developing flat faces
at the sites of near contact, and bodies vanishing. In this nearly
touching bodies structure, we also observe these similar phenomena but
not totally the same.  For the speed of expanding space at the narrow
channel, we see some narrow channels do expand faster than other wider
channels.  For example, the spacing between bodies 14 and 18 is smaller
than the spacing between bodies 7 and 14 initially and the former one is
comparable to the latter one by the second frame. But there are some
small initial spacings that do not expand that much at all by the fourth
frame, for example between bodies 1 \& 6, 3 \& 9.  We could find the
explanation from the vorticity of fluid in Fig.~\ref{fig:Eroding20vort}.
Since the eroding velocity on the body is proportional to the absolute
value of vorticity in our erosion model,  then when the  absolute value
of vorticity is small there is not much erosion on the body.  In all
four frames of Fig.~\ref{fig:Eroding20vort}, the vorticity is relatively
small between bodies 1 \& 6 and 3 \& 9.

Besides the channels between two bodies, there is a single channel goes
across the domain horizontally and the flow has been concentrated in
this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
12, and 6 \& 19.  We can get a better understanding of this channel from
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
tracer) first comes from three small channels between outer wall \& body
10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
one and go into the main channel between bodies 1 \& 9.  From the first
frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
is expanding faster than other channel and bodies 4 \& 12 has vanished
and body 19 is almost gone in the forth frame.  The reason of fast
expansion of this channel is the high vorticity.  In the forth frame of
Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
high on the side of bodies which form this channel so the bodies are
eroded fast on the side of this channel or have vanished completely.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b60}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b90}\\

\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b120}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b150}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b180}\\

\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
  the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.
  The tracers are evenly spread in the $x_2-$direction and released at
  $x_1=-1$.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.3 \textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Fig.~\ref{fig:Eroding20tracer}. The trajectories of tracers
  around the bodies. Since we use a Barycentric quadrature rule and the
  fourth order Runge Kutta method, the tracers can be very close to but
  not penetrate the bodies. }
\end{center}
\end{figure}

>>>>

In~\cite{qua-moo2018}, we observed that erosion causes the space
between nearly touching bodies to quickly expand, and flat faces develop
along the region of near contact.  This qualitative behavior is also
observed In Figure~\ref{fig:Eroding20vort}, such as between bodies 3
\&4 and 15 \& 16.  However, by resolving bodies that are
much closer to one another when compared to our previous
work~\cite{qua-moo2018}, we see that it is possible for very little
erosion to occur between a pair of bodies.  In particular, for pairs of
bodies where the channel between the bodies is nearly perpendicular to
the main flow direction (bodies 1 \& 6, 3 \& 9, and 13 \& 15), there is
very little shear stress and the effect of erosion is slight.

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense101} \\
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.43\textwidth]{./figs/20b_dense301}
%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\
%\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
%\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
  with the fixed pressure drop condition. The color is the vorticity of
  the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
  256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
  and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In
  the forth frame, bodies 4, 12, and 17 have vanished completely, and
  body 19 has almost completely eroded.}
\end{center}
\end{figure}

In this example, we also observe that erosion creates a network of
channels from the inlet to outlet where the velocity and vorticity, and
therefore erosion rate, are much larger than the other regions.  These
channels can be further visualized by considering the streamlines at
several configurations of the eroding body.  In
Figure~\ref{fig:Eroding20tracer}, we simulate 200 tracers that are
initially to the left of the porous region and equispaced in $y$.  There
are two clear region where the tracers pass through the geometry
much faster than the other regions.  To illustrate the ability of the
Barycentric quadrature formula, streamlines very close to the eroding
bodies are illustrated in Figure~\ref{fig:Eroding20zoom}.

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b30}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b60}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b90}\\

\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b120}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b150}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b180}\\

\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b210}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b240}
\includegraphics[width = 0.32 \textwidth]{./figs/tracer_20b270}
\caption{\label{fig:Eroding20tracer}The trajectories of 200 tracers in
  the fluid with 20 bodies. The 9 snapshots are evenly spaced in time.
  The tracers are evenly spread in the $y$-direction and released at
  $x=-1$.}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}

{\color{red} 
Besides the channels between two bodies, there is a single channel goes
across the domain horizontally and the flow has been concentrated in
this channel.  In the second frame of Fig.~\ref{fig:Eroding20vort}, this
channel is between bodies 1 \& 20, 1 \& 9, 4 \& 3, 8 \& 11, 8 \& 2, 6 \&
12, and 6 \& 19.  We can get a better understanding of this channel from
the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}.  In the
top three frames of  Fig.~\ref{fig:Eroding20tracer}, the flow (or
tracer) first comes from three small channels between outer wall \& body
10, bodies 7 \& 14, and bodies 14 \& 18, then the three branches become
one and go into the main channel between bodies 1 \& 9.  From the first
frame to the forth frame of Fig.~\ref{fig:Eroding20vort}, this channel
is expanding faster than other channel and bodies 4 \& 12 has vanished
and body 19 is almost gone in the forth frame.  The reason of fast
expansion of this channel is the high vorticity.  In the forth frame of
Fig.~\ref{fig:Eroding20vort}, we could see the vorticity is relatively
high on the side of bodies which form this channel so the bodies are
eroded fast on the side of this channel or have vanished completely.

@@
